Tropical Andes montane and lowland forest bird and mammal species GBIF

### 2023-07-27 code/L0/L0_TropicalAndes_IUCNhabitatClassification.Rmd
inital commit
change input file reference link

@@

# Load required packages
```{r}
library(raster)
```

# Load in Ecosystem Functional Groups
Data downloaded from www.zendo.org/record/5090419
```{r}
iucn_habitats <- raster(file.path(data_path, "iucn_habitatclassification_composite_lvl2_ver004.tif"))
```

>>>>

---
title: ""
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: ""
data input: "iucn_habitatclassification_composite_lvl2_ver004.tif"
data output: ""
date: "2023-07-18"
output: html_document
---

@@

# Load required packages
```{r}
library(raster)
library(sf)
```

# Load in Ecosystem Functional Groups
Data downloaded from https://zenodo.org/record/5090419                                                                                                 
```{r}
iucn_habitats <- raster(file.path(data_path, "iucn_habitatclassification_composite_lvl2_ver004.tif"))
```

```{r}
plot(iucn_habitats)
```

Crop extent
```{r}

```
